Revealing Benefits, Costs, and Tradeoffs of Spatial Management in Marine Systems Arrising from Coupled Economic and Ecological Dynamics

### 2023-10-24 03_marlin_paper.qmd
pre submission edits

$$
N_{t,p,s,a} = \begin{cases}
      = BH(SSB_{t-1,p,s,a}) & \text{if $a = 1$}\\
     = N_{t-1,p,s,a-1}e^{-(z_{t-1,p,s,a-1}}, & \text{if $1< a < max(age)$}\\
     =  N_{t-1,p,s,a}e^{-(z_{t-1,p,s,a})} + N_{t-1,a-1}e^{-(z_{t-1,p,s,a-1})}, & \text{if $a = max(a)$}
  \end{cases}
$$ {#eq-pop}

@@

>>>>

$$
N_{t,p,s,a} = \begin{cases}
      = BH(SSB_{t-1,p,s,a}) & \text{if $a = 1$}\\
     = N_{t-1,p,s,a-1}e^{-(z_{t-1,p,s,a-1})}, & \text{if $1< a < max(age)$}\\
     =  N_{t-1,p,s,a}e^{-(z_{t-1,p,s,a})} + N_{t-1,a-1}e^{-(z_{t-1,p,s,a-1})}, & \text{if $a = max(a)$}
  \end{cases}
$$ {#eq-pop}

@@

## Figure Legends
